GatorDSR: University of Florida Knowledge Base Acceleration Notebook

### 2013-09-22 paper/kbanotebook2013/content/introduction.tex
Major rewriting of paper in latex + schematic diagram + reference + precision/recall statistics

The task is that given certain Wikipedia or Twitter entities (wiki/twitter URLs) and certain relations of interest given in Table 1, extract as many binary relations as possible (hence, slot filling). The corpus is in English and is a snapshot of part of the web containing arXiv, social, news, linking, weblog, forum, classifieds, reviews, and memetracker documents. Each document is annotated using lingpipe and is called StreamItem, a bundle of StreamItems are put together and serialized as Apache Thrift objects, then compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys. To have a sense of the scale of objects and compression is e.g. 6mb gpg.xz files → 45 mb thrift objects. Some of the documents have null values for their annotation fields.

Since this is \textit{streaming} slot filling, we are only interested in new slot values that were not substantiated earlier in the stream corpus, which ranges from October 2011 to February 2013. Below you can view the slot values and their types, the comprehensive description of which can be found at http://www.nist.gov/tac/
2012/KBP/task\_guidelines/TAC\_KBP\_Slots\_V2.4.pdf and http://projects.ldc.up
enn.edu/ace/docs/English-Events-Guidelines\_v5.4.3.pdf

@@

>>>>

The task is that given certain Wikipedia or Twitter entities (wiki/twitter URLs) and certain relations of interest given in Table 1, extract as many triple relations as possible (hence, slot filling). This can be used to automatically populate knowledgebases such as free-base or DBPedia or even filling in the information boxes at Wikipedia. The corpus is in English and is a snapshot of part of the web containing arXiv, social, news, linking, weblog, forum, classifieds, reviews, and memetracker documents. Each document is annotated using lingpipe and is called StreamItem, a bundle of StreamItems are put together and serialized as Apache Thrift objects, then compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys. To have a sense of the scale of objects and compression as an example a 6mb gpg.xz files would become 45 mb thrift objects which can contain a couple of thousand StreamItems depending on their size. Some of the documents have null values for their annotation fields.

Since this is \textit{streaming} slot filling, we are only interested in new slot values that were not substantiated earlier in the stream corpus, which ranges from October 2011 to February 2013. Below you can view the slot values and their types, the comprehensive description of which can be found at \cite{tackbp} and \cite{aec}

@@

In our approach we will perform pattern matching that conforms to each slot value along with post-processings to eliminate noisy outputs.

### 2013-09-22 paper/kbanotebook2013/content/system.tex
Major rewriting of paper in latex + schematic diagram + reference + precision/recall statistics

\section{System}
% Note: Describe the algorithms of each phase
% Talk in abstract terms not implementation.
% Use formal representations (Math, SQL etc)

\subsection{Cumulative Citation Recommentation}

@@

@@

>>>>

\begin{figure}[b]
\centering
\includegraphics[width=4.5in]{./images/system.eps}
\vspace*{-.1in} \caption{Pipeline Design }\label{fig:system}
\vspace*{-.2in}
\end{figure}

\section{Pipeline}

In this section we provide a high level description of the pipeline(system) design for big data analysis regarding TREC KBA the Stream Slot Filling (SSF) task. Our pipeline of processing the corpus consists of a two layer indexing system main section in our system regarding indexing the corpus, We started off by trying to use the off-the-shelf tools for this task. Mainly we started by using Scala/Spark\cite{ferc11} to benefit from the paralellization performance there.  Spark was not as efficient as expected and the overhead was much more than tolerable. We tried to use Scala parallelization itself to do the job, and unfortunately it did not satisfy our needs, there was excessive memory overhead on map reduce jobs. We migrated the core of the system to Java Parallelism APIs and that was not good enough either, we wanted better. So we built our own parallel system which in actual performance had the least of overhead, the least memory consumption and the most robust memory model which avoided unpredictable CPU stalls on garbage collections in processing the corpus. In what follows we will describe each step of this evolution in details. Figure \ref{fig:system} shows a schematic view of the system. The platform that we run our pipeline over was a 32 core server having 64GB of memory.

% Note: Describe the algorithms of each phase
% Talk in abstract terms not implementation.
% Use formal representations (Math, SQL etc)

\subsection{Cumulative Citation Recommendation}

Regarding Cumulative Citation Recommendation we perform exact string matching and treat all the documents that mention an entity equally likely to be citable. For future iterations of the paper we have ideas on how to score documents based on their likelihood of citation worthiness but for this iterations we treat all mentioning documents equally likely. One of the reasons for this is that in former TREC KBA reports \cite{JFrank12} there were observations of how non-mentioning documents have highly low chance of being citeable in wikipedia. So we take on that and ignore non-citing documents. Regarding mentioning but garbage, neutral or central documents we produce more slot values which can be later on filtered out in the high accuracy filter section.

@@

Stream slot filling is done by pattern matching documents with manually produced patterns for slots of interest. The way we do this is by observing a sentence that has a mention of the entity or one of its coreferences. An anchor word in the sentence related to the slot name is located and we match either left or right of the anchor word for potential slot values.

@@

The SSF output of many extractions is noisy. The data contains duplicates and incorrect extractions. We can define rules to sanitize the output only using the information present in the SSF file. The file is processed in time order, in a tuple-at-a-time fashion to minimize the impact on accuracy. . We define two classes of rules deduplication rules and inference rules.
